Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-18 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Adds data on fit
Citations added

\subsection{$F_{15}:\frac{D}{m}$-group Shifted and $m$-rotated Rastrigins Function}
JavaScript has been traditionally implemented as an interpreted
language not designed for the development of high performance
systems. On the other hand, current JavaScript  
virtual machines (VMs) are closing the gap, for instance the Google V8 
is an engine specifically designed for the fast execution of 
large JavaScript applications. In order to increase performance
V8 compiles JavaScript source code directly into machine code when it is first executed. 
There are no intermediate byte codes or an interpreter.
[\url{ https://developers.google.com/v8/design#mach_code}].
JavaScript has gained popularity in server-side development using runtime
environments such as Node.js and is also used in desktop and mobile applications. 
%Mario: Creo que el párrafo de arriba sale sobrando
To further evaluate how a current JavaScript implementation could be used by a
computer scientist to develop complex optimization problems,
a benchmark function, which was provided by the CEC2010 Special Session on
Large-Scale Global Optimization [] is used in this section. 
The function is described next.

@@

%
\begin{figure}[!htb]
\centering
\includegraphics{rastrigin-fitness.png}
\caption{Fitness of chromosomes sent to the server pool along time in
  the $x$ axis.} 
% Plotted with ../data/plot-rastrigin-fitness.R
\label{fig:puts:rastrigin}
\end{figure}
%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.49\linewidth]{rastrigin-IPs.png}
\includegraphics[width=0.49\linewidth]{rastrigin-ips-hour.png}
\caption{Number of unique IPs participating in the Rastrigin
  experiment per minute (left) and per hour (right)} 
% Plotted with ../data/plot-rastrigin-IPs.R
\label{fig:ips:rastrigin}
\end{figure}

>>>>

\subsection{$F_{15}:\frac{D}{m}$-group Shifted and $m$-rotated Rastrigins Function}
JavaScript has been traditionally implemented as an interpreted
language not designed for the development of high performance
systems. On the other hand, current JavaScript  
virtual machines (VMs) are closing the gap, for instance the Google V8 
is an engine specifically designed for the fast execution of 
large JavaScript applications. In order to increase performance
V8 compiles JavaScript source code directly into machine code when it is first executed. 
There are no intermediate byte codes or an interpreter \cite{Gray:2009:GCM:1610564.1610565}.
JavaScript has gained popularity in server-side development using runtime
environments such as Node.js and is also used in desktop and mobile applications. 
%Mario: Creo que el párrafo de arriba sale sobrando
To further evaluate how a current JavaScript implementation could be used by a
computer scientist to develop complex optimization problems,
a benchmark function, which was provided by the CEC2010 Special Session on
Large-Scale Global Optimization \cite{tang2007benchmark} is used in this section. 
The function is described next.

@@

%
\begin{figure}[!htb]
\centering
\includegraphics{rastrigin-fitness.png}
\caption{Fitness of chromosomes sent to the server pool along time in
  the $x$ axis.} 
% Plotted with ../data/plot-rastrigin-fitness.R
\label{fig:puts:rastrigin}
\end{figure}
%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.49\linewidth]{rastrigin-IPs.png}
\includegraphics[width=0.49\linewidth]{rastrigin-IPs-hour.png}
\caption{Number of unique IPs participating in the Rastrigin
  experiment per minute (left) and per hour (right)} 
% Plotted with ../data/plot-rastrigin-IPs.R
\label{fig:ips:rastrigin}
\end{figure}
%
\begin{table*}
\caption{Summary of fit to Generalized Extreme Value (GEV) and Weibull distribution of
  the number of {\tt PUT}s per worker for the F15 (Rastrigin) function. \label{tab:puts:ww:f15}}
\begin{center}
\begin{tabular}{cccc}
\hline
Distribution & Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
GEV & 35.759 $\pm$ 0.83719  &  343.336  $\pm$  & 9.877   $\pm$
0.04746 \\
Weibull & ND & 29.002625061 $\pm$ 2.153034198  & 0.402393903 $\pm$ 0.007586468 \\
\hline
\end{tabular}
\end{center}
\end{table*}
